Open archaeology, open source?

### 2023-09-20 analysis/_01-introduction.qmd
Comment on introduction text

The relationship between open science and open source is also complicated by rhetorical claims that, based on our personal experiences, are discordant with how academics actually _do_ open source. Does academic open source actually make research processes more transparent and improve research outcomes? Is it actually boosting efficiency by establishing a common store of knowledge and productive code? Is it actually helping to foster new globe-spanning connections and lead to novel research trajectories that would not otherwise come to pass? Despite hopeful aspirations espoused by open archaeology advocates [see @kansa2014; @kintigh2015], these outcomes are not a given. We believe that these outcomes only actually arise in contexts where participants adhere to and are motivated by warrants, professional norms, and governance strategies that encourage these results. However, practical circumstances and systemic value regimes that frame what it means to work as an archaeologist presently inhibit the potential for radical transformation, even among open science's most ardent supporters.

That being said, archaeologists are prolific software developers. This is made evident by open-archaeo, a comprehensive list of open source archaeological software and resources that indexes XXX records as of the time of publication. But beyond simply making their code available on the web, do archaeologists also implement social strategies to advance open source ideals? Does archaeological open source actually help achieve greater transparency, sustainability, and community participation? And if not, what does it actually achieve?

>>>>

The relationship between open science and open source is also complicated by rhetorical claims that have a questionable connection to how academics actually _do_ open source. 
Does academic open source actually make research processes more transparent and improve research outcomes? 
Is it actually boosting efficiency by establishing a common store of knowledge and productive code? 
Is it actually helping to foster new globe-spanning connections and lead to novel research trajectories that would not otherwise come to pass?
Basically, is it more than just uploading code and data files to the internet?

Despite hopeful aspirations espoused by open archaeology advocates [see @kansa2014; @kintigh2015], these outcomes are not a given. We believe<!-- Bit weak; can we cite some previous work that indicates this? --JR---> that these outcomes only actually arise in contexts where participants adhere to and are motivated by warrants, professional norms, and governance strategies that encourage these results. However, practical circumstances and systemic value regimes that frame what it means to work as an archaeologist presently inhibit the potential for radical transformation, even among open science's most ardent supporters.

<!-- Might be getting a bit ahead of ourselves here. --JR -->That being said, archaeologists are prolific software developers. This is made evident by open-archaeo, a comprehensive list of open source archaeological software and resources that indexes XXX records as of the time of publication. But beyond simply making their code available on the web, do archaeologists also implement social strategies to advance open source ideals? Does archaeological open source actually help achieve greater transparency, sustainability, and community participation? And if not, what does it actually achieve?
